Optimal (Multiway) Spatial Joins

### 2024-05-30 4.3.tex
4.3
yufei

% First, we prove (1). For any $i \in [k-2]$, $r_i^*\in R_i^*$, and $h \in \cross_H(r_i^*)$, we will identify a unique tuple $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$ such that $\bm{t}[k-1] = h$, and $\bm{t}[i]$ is the full rectangle of $r_i'$, whose top-sliced rectangle is $r_i^*$. Let $\maxtop(r_i') = \ytop(B_\bm{t'})$ for some tuple $\bm{t'} \in \J(R_1',...,R_{k-2}')$. Let $\bm{t'} = (r'_1,...,r'_{k-2})$, and let $r_i$ be the full rectangle of $r_i'$ for $i \in [k-2]$. Since $h$ crosses $r_i^*$, and $B_\bm{t'} \subseteq r_i^*$, $h$ crosses $B_{\bm{t'}}$. Let $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. The intersection of $h$ and $v$ is a point on the left boundary of $B_{\bm{t'}}$, which means that $h\cap v \in B_{\bm{t'}} \subseteq \cap_{i = 1}^{k-2}r_i$. Therefore, $\bm{t} = (r_1,...,r_{k-2},h,v)\in \J(R_1,...,R_{k-2},H,V)$ is the desired tuple, and we have $\sum_{i \in [k-2]}\sum_{r_i^*\in R_i^*} |\cross_H(r_i^*)| \leq \out$.

% Next, we prove (2). Let $r' = [x_1,x_2]\times [y_1,y_2]$, and $r^* = [x_1,x_2] \times [y_1,\maxtop(r')]$. Since $\gbot(\bm{t}) = r'$, $\dcross_H(\bm{t})$ contains exactly the set of segments segment $h \in H$ that cross the rectangle $[x_1,x_2]\times [y_1, \ytop(B_\bm{t})]$, where $\ytop(B_{\bm{t}})\leq \maxtop(r')$. Therefore, $\dcross_H(\bm{t})$ $\subseteq \cross_H(r^*)$. Furthermore, if the (horizontal) segments of $\cross_H(r^*)$ are sorted in ascending order of y-coordinate, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.

\noindent \underline{\em Proof of Statement (2).}

>>>>

\noindent \underline{\em Proof of Statement (2).} 
Let $r' = [x_1,x_2] \times [y_1,y_2]$. Then, $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$. Let $h$ be an arbitrary segment in $\dcross_H(\bm{t})$, whose y-coordinate is $y_h$.  We will prove that $h$ crosses $r^*$, which leads to $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. It suffies to show that $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$. 
\begin{itemize}
    \item Since $h$ crosses $r' = [x_1,x_2]\times [y_1,y_2]$, we have $\xleft(h) < x_1 \le x_2 < \xright(h)$.
    \item Since $h$ crosses $B_{\bm{t}}$, we have $y_h \in [y_1, \ytop(B_{\bm{t}})]$. By the definition of $\maxtop(r')$ (see Definition \eqref{eqn:hv:type1:maxtop}), and the fact that $r' = \gbot(B_{\bm{t}})$, we have $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. Therefore, $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}

\vgap

Then, we will prove that each segment $h \in \cross_H(r^*)$ satisfying that the y-coordinate $h$ is no more than $\ytop(B_{\bm{t}})$ is in $\dcross_H(\bm{t})$. This claim leads to the last sentence of Statement (3). Consider an arbitrary $h\in \cross_H(r^*)$, whose y-coordinate $y_h$ satisfies that $y_h \le \ytop(B_{\bm{t}})$. We will prove that $h$ crosses $r'$ and $B_{\bm{t}}$, and therefore $h \in \dcross_H(\bm{t})$.

\vgap

First, we prove that $h$ crosses $r'$. It suffices to show that $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. Both conditions are satisfied since $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$. Then, we prove that $h$ crosses $B_{\bm{t}}$. It suffices to show that $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item Since $h$ crosses $r'$, we have $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$. 
\end{itemize}
